Coexistence with varying environmental filtering intensity

### 2018-07-02 env_intensity.Rmd
:art: Plot CWM for all traits + number ind
Co-authored-by: Rekyt <matthias.grenie@ens-lyon.fr>
Co-authored-by: pierredenelle <pierre.denelle@cefe.cnrs.fr>

# Generate traits --------------------------------------------------------------
set.seed(1)
traits <- generate_cor_traits(patches, n_traits - 1, cor_coef = 0.7)
colnames(traits) <- paste0("trait", seq(n_traits))
rownames(traits) <- paste0("species", seq(species))

@@

lalaland = ggplot(all_land, aes(compet_dist, optim_dist)) +
    stat_summary_2d(aes(z = N)) +
    facet_wrap(~simulation_type) +
    scale_fill_viridis_c(trans = "log10") +
    scale_x_reverse() +
    labs(x        = "Distance to Maximum Competition\n(0 = species experiences maximum competition)",
         y        = "Distance to Optimal Environmental Value",
         fill     = "Number of Individuals at t=150",
         subtitle = "Growth and Competition Landscape") +
    theme_bw() +
    theme(legend.position = "bottom")

plot_laughlin = ggplot(all_land, aes(optim_env, patch_optim)) +
    stat_summary_2d(aes(z = N)) +
    facet_wrap(~simulation_type, labeller = c(R2_A8 = "20% Growth\n80% Competiton",
                                              R5_A5 = "50% Growth\n50% Competiton",
                                              R8_A2 = "80% Growth\n20% Competiton") %>%
                   as_labeller()) +
    scale_fill_viridis_c(trans = "log10") +
    labs(x    = "Species Optimum",
         y    = "Environmental Value",
         fill = "Number of Individuals") +
    theme_bw() +
    theme(legend.position = "bottom")
```

>>>>

# Generate traits --------------------------------------------------------------
set.seed(1)
traits <- generate_cor_traits(patches, n_traits - 1, cor_coef = 0.3)
colnames(traits) <- paste0("trait", seq(n_traits))
rownames(traits) <- paste0("species", seq(species))

@@

# A plot showing the number of individuals at t=150 depending on the distance
# to the environmental optimum (y-axis), and the distance to the trait
# experiencing maximum competition (x-axis)
plot_dist_compet_dist_env = ggplot(all_land, aes(compet_dist, optim_dist)) +
    stat_summary_2d(aes(z = N)) +
    facet_wrap(~simulation_type) +
    scale_fill_viridis_c(trans = "log10") +
    scale_x_reverse() +
    labs(x        = "Distance to Maximum Competition\n(0 = species experiences maximum competition)",
         y        = "Distance to Optimal Environmental Value",
         fill     = "Number of Individuals at t=150",
         subtitle = "Growth and Competition Landscape") +
    theme_bw() +
    theme(legend.position = "bottom")

# data.frame containing CWM values for all the traits, as well as growth-related
# traits (optim_env) for each patch and each simulation scenario
cwm_patch_trait = all_land %>%
    inner_join(traits %>%
                   as.data.frame() %>%
                   rownames_to_column("species"),
               by = "species") %>%
    group_by(simulation_type, patch) %>%
    mutate(rel_abund = N/sum(N)) %>%
    ungroup() %>%
    gather("trait_name", "trait_value", contains("trait"), optim_env) %>%
    group_by(simulation_type, patch, trait_name) %>%
    summarise(cwm_trait = sum(rel_abund*trait_value),
              patch_optim = mean(patch_optim))

# Plot of Trait CWM in function of environmental value, colored by scenario
plot_cwm = ggplot(cwm_patch_trait, aes(patch_optim, cwm_trait,
                                       color = simulation_type)) +
    geom_abline(slope = 1, intercept = 0, linetype = 2) +
    geom_point(size = 1.5) +
    geom_smooth(method = "lm", se = FALSE) +
    facet_wrap(~trait_name, ncol = 3) +
    labs(x     = "Environmental Value",
         y     = "CWM of Trait",
         color = "Scenario") +
    scale_color_discrete(labels = c(R2_A8 = "20% Growth\n80% Competiton",
                                    R5_A5 = "50% Growth\n50% Competiton",
                                    R8_A2 = "80% Growth\n20% Competiton")) +
    theme_bw() +
    theme(legend.key.height = unit(2, "lines"))
plot_cwm

# Plot showing the number of individuals at t=150 for each trait and each
# environmental value
plot_individuals_trait_environment = all_land %>%
    inner_join(traits %>%
                   as.data.frame() %>%
                   rownames_to_column("species"),
               by = "species") %>%
    gather("trait_name", "trait_value", contains("trait"), optim_env) %>%
    ggplot(aes(trait_value, patch_optim)) +
    stat_summary_2d(aes(z = N)) +
    facet_grid(trait_name ~ simulation_type,
               labeller = labeller(simulation_type =
                                       c(R2_A8 = "20% Growth\n80% Competiton",
                                         R5_A5 = "50% Growth\n50% Competiton",
                                         R8_A2 = "80% Growth\n20% Competiton"))) +
    scale_fill_viridis_c(trans = "log10") +
    labs(x = "Trait Value",
         y = "Optimal Trait Value",
         fill = "Number of Individuals") +
    theme_bw()
```
